Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-22 paper/paper.tex
#28 begin writing baseline results

\subsection{Differential effects of switching}

Next I attempt to identify the effect of state power --- the effect of the difference in selection for state power between conquests and successions. In the best case, if the identifying assumption is satisfied, the estimates from the previous regression tell us what the effect of switching states is - however, they cannot tell us why.

Because the \textit{Städtebuch} data compiled by \cite{pt2} records exactly how each city was acquired by the territory holding it, I am able to look at differential trends after different types of ownership changes.\footnote
{
Presumably \cite{schoenholzer2022}, having sourced their data on territorial histories from historical maps, lack detailed information about individual switching events. They instead use clever panel decomposition methods (pp. 14-20) and data on state-level characteristics (pp. 21-23) to explain what drives their estimates.
}
For this purpose I extend Equation \eqref{eq:sw22} by interacting the treatment indicator with the type of switching event:
\begin{equation}
\label{eq:baseline}
\begin{split}
    construction_{it} &= \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta +
    \mathbf{1}(t \ge e^{NewState}_i)\pi \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Conquest_{it}) \times \theta_{conquest} \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Other_{it}) \times \theta_{other} + \varepsilon_{it},
\end{split}
\end{equation}

@@

\subsection{More construction events after switching states}

Table \ref{tab:SW22_replication_50y} contains estimates from Equation \eqref{eq:sw22}. Each column reports the effect of switching states on a different subset of observed construction activity: Column (1) for all types of buildings, Column (2) for administrative, military and representative buildings, Column (3) for private construction, and Column (4) for buildings that provide public goods. The exact definitions of these categories are as described in Section \ref{sec:data}.

We can see in Column (1) that switching states has no immediate effect (relative to the period that precedes the switch) on the probability of recorded construction activity; over the following 200 years, however, the effect grows positive and significant.

Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise how the effect evolves dynamically.

>>>>

\subsection{Heterogeneous effects of switching}

In the best case, if the identifying assumption is satisfied, the estimates from the previous regression tell us what the effect of switching states is --- however, they cannot tell us why. In the following I attempt to identify the effect of state power, or more accurately, the effect of the difference in selection for state power between conquests and successions.

Because the \textit{Städtebuch} data compiled by \cite{pt2} records exactly how each city was acquired by the territory holding it, I am able to estimate differential trends after different types of ownership changes.\footnote
{
Presumably \cite{schoenholzer2022}, having sourced their data on territorial histories from historical maps, lack detailed information about individual switching events. They instead use clever panel decomposition methods (pp. 14-20) and data on state-level characteristics (pp. 21-23) to explain what drives their estimates.
}
For this purpose I extend Equation \eqref{eq:sw22} by interacting the treatment indicator with the type of switching event:
\begin{equation}
\label{eq:baseline}
\begin{split}
    construction_{it} &= \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta +
    \mathbf{1}(t \ge e^{NewState}_i)\pi \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Conquest_{it}) \times \theta_{conquest} \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Other_{it}) \times \theta_{other} + \varepsilon_{it},
\end{split}
\end{equation}

@@

\subsection{Construction activity increases after switching states}

Table \ref{tab:SW22_replication_50y} contains estimates for the coefficients $\pi_\tau$ from Equation \eqref{eq:sw22}. Each column reports the effect of switching states on a different subset of observed construction activity: Column (1) for all types of buildings, Column (2) for administrative, military and representative buildings, Column (3) for private construction, and Column (4) for buildings that provide public goods. The exact definitions of these categories are as described in Section \ref{sec:data}. Note also that a $Period$ is an interval of 50 years that begins with the given year. $Period = -50$ is omitted as the reference category for treated cities. Reassuringly, as the coefficients on $Treat \times Period = -100$ show, there are no significant pre-trends in any of the outcome variables.

We can see in Column (1), beginning  that switching states has no immediate effect on the probability of recorded construction activity. Over the next two centuries, however, the effect grows positive and significant: 100 years after a city switches states, the probability of construction activity is 5 percentage points higher than in cities that did not switch. After 200 years this difference grows to 9 percentage points. These estimates are significant at the 5 percent and 1 percent level, respectively. Figure \ref{fig:SW_replication} plots the coefficients in Column (1) to visualise these dynamics.

By contrast, almost all the coefficients in Columns (2), (3) and (4) are insignificant, suggesting that no particular subset of construction is driving the results.

\subsection{No evidence for the state power hypothesis}

Table \ref{tab:baseline_50y} shows estimates from Equation \eqref{eq:baseline}. This is a difference-in-differences specification with interactions to capture heterogeneous treatment effects. As before, different columns use different subsets of construction as the outcome variable.

I report estimates of the coefficient of interest $\theta_{conquest}$ in the second row.
